The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-12-02 paper/paper.qmd
update paper

This research seeks to fill this gap by systematically investigating the role of various disruptions during social survey interviews, focusing particularly on how different types of familial and environmental interferences affect respondent comprehension and engagement. To this end, we conducted a comprehensive analysis using Bayesian hierarchical logistic regression, implemented through the rstanarm package in R. This model structure was chosen for its ability to capture complex relationships, accounting for multiple levels of influence—namely, disruptions at the respondent level and interviewer characteristics nested within the survey context. The use of Bayesian methods allowed us to incorporate prior knowledge and manage uncertainty in the analysis effectively, while also making inferences about the likely impacts of the disruptions on data quality. Throughout the data preparation phase, categorical variables were simplified, excluding variables like 'country' that introduced excess complexity, in order to enhance interpretability and ensure the model’s tractability. Additionally, predictor variables included the method of interview administration (e.g., telephone, in-person), interviewer characteristics (age and gender), and respondent attitudes (such as willingness to answer or the need for clarification), providing a comprehensive understanding of the factors influencing survey outcomes.

>>>>

This research seeks to fill this gap by systematically investigating the role of various disruptions during social survey interviews, focusing particularly on how different types of familial and environmental interferences affect respondent comprehension and engagement. To this end, we conducted a comprehensive analysis using Bayesian hierarchical logistic regression, implemented through the rstanarm package in R. This model structure was chosen for its ability to capture complex relationships, accounting for multiple levels of influence—namely, disruptions at the respondent level and interviewer characteristics nested within the survey context. The use of Bayesian methods allowed us to incorporate prior knowledge and manage uncertainty in the analysis effectively, while also making inferences about the likely impacts of the disruptions on data quality.
